\mytitle

### 2021-12-07 paper.tex
extend text

As an application we consider the implementation of the real
dilogarithm, which appears in many physics applications, for example
in the calculation of quantum corrections in quantum electrodynamics.
The real dilogarithm is defined as
%
\begin{align}
  \Li(x) &= -\int_0^x \frac{\log(1-t)}{t}dt, &
  &(x<1).
\end{align}
%
For $|x|<1$ the real dilogarithm has the series representation
%
\begin{align}
  \Li(x) = \sum_{k=1}^\infty \frac{x^k}{k^2}.
\end{align}
%
Further series representations exist, for example the accelerated
series
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty \frac{B_k}{(k+1)!} [-\log(1-x)]^{k+1},
\end{align}
%
where $B_k$ are the Bernoulli numbers.  A series representation in
terms of Chebyshev polynomials of the first kind $T_n(x)$ is given in
\cite{luke},
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty a_n T_n(2x-1),
  \label{eq:cheby}
\end{align}
%
which is used for example in the ROOT program library \cite{root}.

>>>>

As an application we consider the implementation of the real
dilogarithm, which appears in many physics applications, for example
in the calculation of quantum corrections in quantum electrodynamics.
The real dilogarithm is defined as
%
\begin{align}
  \Li(x) &= -\int_0^x \frac{\log(1-t)}{t}dt, &
  &(x<1).
\end{align}
%
For $|x|<1$ the real dilogarithm has the series representation
%
\begin{align}
  \Li(x) = \sum_{k=1}^\infty \frac{x^k}{k^2}.
  \label{eq:series}
\end{align}
%
Further series representations exist, for example the accelerated
series
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty \frac{B_k}{(k+1)!} [-\log(1-x)]^{k+1},
\end{align}
%
where $B_k$ are the Bernoulli numbers.  A series representation in
terms of Chebyshev polynomials of the first kind $T_n(x)$ is given in
\cite{luke},
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty a_n T_n(2x-1),
  \label{eq:cheby}
\end{align}
%
which is used for example in the ROOT program library \cite{root}.
Eqs.~\eqref{eq:series}--\eqref{eq:cheby} can be summed, for example
using Horner's scheme or Clenshaw's algorithm \cite{clenshaw}.  These
summation techniques are, however, purely sequential and thus do not
make use of ILP.  In the following an approximation of the real
dilogarithm is presented, which makes use of ILP, using a rational
function approximation in combination with Estrin's scheme, similarly
to the approach use in Eq.~\eqref{eq:mixed}.
